A \proglang{Python}/\proglang{Zig} optimized and customizable implementation for the $\rho_{DCCA}$ and $DMC_x^2$ methods

### 2025-03-07 paper_v02/article.tex
comparisson table

>>>>

The algorithm was tested with data and results from the \cite{RIBEIRO2025107419} paper, the original data came from the \textit{Physionet} open-access website, available at this link:

\begin{center}
	\url{https://physionet.org/content/eegmmidb/1.0.0/}
\end{center} 
This comprehensive dataset of EEG (electroencephalogram) data, with 108 subjects, executing 12 experiments each, with the $\rho_{DCCA}$ and $DMC_{x}^{2}$ calculated for all experiments, using signals from four electrodes. The results were compared with the original ones, and the algorithms where validated.

Regarding performance, the pure \proglang{Python} implementation, the \proglang{Zig} implementation and the optimized \proglang{Zig} where compared with 3 oder packages that calculates the $\rho_{DCCA}$. Researching the \proglang{R} \textbf{CRAN} package repository, the \pkg{DCCA} \pkg{DFA} packages where found, and, from the \proglang{Python} \textbf{pypi}, the \pkg{DCCA} package was used.

The \pkg{DFA}~\citep{R-DFA} is a pure \proglang{R} implementation. The \pkg{DCCA}~\citep{R-DCCA} is a \proglang{R} package implemented in \proglang{Java}. A package also named \pkg{DCCA}\citep{alchieri2024lateralization} is a \proglang{Python} implementation with massive use of \pkg{Numpy} broadcasting capabilities and memory access with strides to avoid loops.

\begin{table}[h]
  \centering
  \caption{Elapsed Time Comparison}
  \begin{tabular}{@{}l@{\hspace{1.0cm}}l@{\hspace{1.0cm}}l@{\hspace{1.0cm}}l@{}}
    \hline
    Package & Implementation & Elapsed Time(s) & Percentage Increase \\
    \hline
    Zebende & Zig (opt) & 27.52  & - \\
    Zebende & Zig (basic) & 42.03 & 52.7\% \\
    DCCA & Python & 370.54 & 1239.4\% \\
    DCCA & R-Java & 1987.67 & 7202.4\% \\
    Zebende & Pure Python & 2415.94 & 8803.4\% \\
    DFA & R & 20173.13 & 73,011.4\% \\
    \hline
  \end{tabular}
\end{table}

Regarding performance
